A Survey on Ordered Binary Decision Diagrams

### 2015-09-08 paper.tex
Add BDD description

>>>>

\textit{Binary decision diagrams} (\textit{BDDs}) have been well studied since
Lee~\cite{LEE59} and especially Akers~\cite{AKERS78} introduced them. BDDs
represent a Boolean function $f$ as an acyclic, directed graph (DAG). Nodes
represent variables and have one incoming and two outgoing edges, each of which
denotes the variable evaluates to 0 (left) or 1 (right), respectively. There exist
two \textit{terminal} nodes, denoted \textbf{0} (\textbf{False}) and \textbf{1}
(\textbf{True}), which represent the result of $f$. To evaluate $f$ for a given
variable assignment, one just follows the path for the respective variable values
and the terminal nodes one exists is the result.
\tbr
